Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-04-30 tese/section01.tex
added more bibliography
jitsi stuff

\ac{WebRTC} uses \ac{UDP} for transporting data, which provides lower latencies than \ac{TCP}, but is not reliable and packet order and integrity are not assured. \ac{SCTP} and \ac{SRTP} are used for streaming data, providing a mechanism for congestion control and partial reliable delivery over \ac{UDP}. All transferred audio, data,  and video must be encrypted with \ac{DTLS} which provides the same security guarantess as \ac{TLS}.

@@

>>>>

\ac{WebRTC} uses \ac{UDP} for transporting data, which provides lower latencies than \ac{TCP}, but is not reliable and packet order and integrity are not assured. \ac{SCTP} and \ac{SRTP} are used for streaming data, providing a mechanism for congestion control and partial reliable delivery over \ac{UDP}. All transferred audio, data and video must be encrypted with \ac{DTLS} which provides the same security guarantess as \ac{TLS}.

@@

Jitsi Meet\footnote{jitsi meet} is a \ac{WebRTC} collaborative application that uses Jitsi Videobridge for high quality and scalable video conferences and supports shared document editing. Jitsi Videobridge is a server that enables multiparty video calls.

### 2015-04-30 tese/section04.tex
jitsi stuff

@@

>>>>

  {\color{red}[DTLS and SRTP]}

@@

	Multiparty video calls can be achieved on \ac{WebRTC} by streaming video from each participant to all the other participants. Although this works, the bigger a conference room is, the bigger is the bandwidth used to stream video to all participants within the conference room.

	Jitsi Video Bridge \footnote{jitsi VB} receives one stream from every participant on a conference, either from a jitsi client or a \ac{WebRTC} application, and redirects it to all the other conference participants, reducing the amount of data that each peer sends. Although all the participants need to download all the streams from Jitsi Video Bridge Server, typically download rates are much bigger than upload rates, making this solution more feasible.

	Jitsi Video Bridge uses \ac{XMPP} as a signaling protocol and its colibri extension (XEP-0340) to reserve channels for video transmission. Although this choice for signalling protocol, Jitsi Video Bridge also supports \ac{SIP} and \ac{Jingle}.
